---
title: "Basic_Exploration_RMarkdown"
author: "Paul Apivat Hanvongse"
date: "8/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Actual Exploration

The primary thing for you to know about RMarkdown (for now) is that its a format that you can use to run your analysis and, most importantly, communicate your findings to your stakeholders. 

First, we will do some fundamental things that you'll want to do at the start of *every* data handling session. 

Note the difference between "white" area and "light gray" areas (code chunks).

```{r, echo=FALSE}

# Good Practice: Run sessionInfo() to make a note of software version you're using
sessionInfo()

# Libraries and Packages 
install.packages('tidyverse')
library(tidyverse)
library(readxl)
install.packages('reshape2')
library(reshape2)

```

## U.N. Statistics: Loading and Reading Data

We will be exploring Sustainable Development Goals Indicator [statistics](https://unstats.un.org/sdgs/indicators/database/). While there are a variety of indicators and goals, we'll focus our basic data exploration on Goal 4, "Ensure inclusive and equitable quality education and promote lifelong learning opportunities for all", Target 4.4, "By 2030, substantially increase the number of youth and adults who have relevant skills, including technical and vocational skills, for employment, decent jobs and entrepreneurship". 

Here we'll read in the data that is in Excel format. I've stored raw data in the 'data' folder for this project (see Files section --> )

Several things are going on at once here, I explain in the comments. Comments are preceded below by a hash tag '#'.


```{r, include=FALSE}

# the read_xlsx() function is used to denote file path to the raw data
# reads data and assign / save to 'data'

data <- read_xlsx("./data/sdg_goal_4.4.xlsx")


# glimpse() function is used to preview the data

glimpse(data)
```

## YOUR TURN: Loading and Reading Data

Now is your chance to practice.

```{r, include=FALSE}

# Use the read_xlsx() function to read another file called 'sdg_goal_4.4_clmv.xlsx'
# Click into the data directory to see
# read the data, then assign (save) to a variable called "data_clmv"

# your code here
data_clmv <- read_xlsx("./data/sdg_goal_4.4_clmv.xlsx")



# Use the glimpse() function to quickly look at your data
# select and run data_clmv inside glimpse()

# your code here
glimpse(data_clmv)

```



## Exploring the Data

In this section we'll use basic commands that come with "Base" R to get a feel for our data. We'll start with the aptly named `glimpse()` function to give you a peek at the data; you'll note the *number* of Rows and Columns. You'll note the column names `$ Column Name` and the `data type` (i.e., dbl, chr, lgl).

If you just want column names, you'll use the `names()` function. If you just want number of rows and columns, you can use `dim()`.

The `View()` or `view()` will open up another tab to visually *show* you your data in spreadsheet format. If you're used to Excel, this will look most like an excel sheet. 

The `str()` function provides slightly more info than `glimpse()`. Namely the *data type* of the data object itself: 'S3: tbl_df / tbl / data.frame'.

```{r, include=FALSE}

# The aptly named glimpse() function allows you to get a glimpse of the data
glimpse(data)

# If you just want column names
names(data)
colnames(data)

# If you just want the number of rows and columns, use dim()
dim(data)

# The View() command allows you to see the data in 'spreadsheet' like format. This is called a data frame or tibble.  Alternatively, you can also click on the data object in the Global Environment.

# View()
View(data)
# view()
data %>% view()

# str() is a function that provides another snapshot preview of the object
# str() provides the internet structure of an R object
# provides more info than glimpse()
str(data)


# there is some overlap with glimpse() and str(), additionally, for numeric data, the summary() function provides quick descriptive statistics (Min, Median, Mean, Max, Quartile)
summary(data)
```

## YOUR TURN: Exploring the Data

```{r,include=FALSE}

## Print out column names for data_clmv
names(data_clmv)
colnames(data_clmv)

## What if you just want number of rows and columns?
dim(data_clmv)

## What if you want to 'see' your data?
View(data_clmv)


## What if you want a snapshot preview with some information about each variable? (hint: internal structure of R object)
str(data_clmv)


## What if you want statistical distribution of numeric variables in your object?
summary(data_clmv)
```

## Missing Data

If you click on the 'spread sheet' view of the data, using `View()` or clicking in the Global Environment panel, you can see for yourself that some columns have 'NA'. But you still want a way to explore exactly how many 'NA' are in each column.

Note, we're now going to be doing something called 'piping' `%>%` where we use multiple functions in successive order on a data object. This functionality `%>%` is possible with the `tidyverse` library (see above), which is the most popular R package and one that we'll use heavily.

Here, we cover two approaches to finding NAs values in your columns - the tedious way and the more efficient way. 

The tedious way is better for learning. So we'll break it down first, then show you the quick way which combines several elements so you'll have to memorize a few things. 

The tedious way requires we take 'data', pipe into `summarize()` function and create variables like `goal_na`, which I take to mean the NAs in the `Goal` column. It is set equal to `sum()`, which contains `is.na()`

```{r, include=FALSE}

# Finding missing values in the Goal column
data %>%
  summarize(goal_na = sum(is.na(Goal)))


# Tedious way of finding NA in each column, one-by-one
data %>%
    summarize(
        goal_na = sum(is.na(Goal)),
        target_na = sum(is.na(Target)),
        indicator_na = sum(is.na(Indicator)),
        timecoverage_na = sum(is.na(TimeCoverage)),
        upperbound_na = sum(is.na(UpperBound))
    )

# Efficient way of finding all NA's for each column
data %>%
  summarize_all(~ sum(is.na(.)))


?is.na
```

## YOUR TURN: Missing Data

```{r, include=FALSE}

## Find number of missing values for the following columns:
## GeoAreaName, Sex, TimeCoverage, Type of skill, Footnote

data %>%
  summarize(
    geoareaname_na = sum(is.na(GeoAreaName)),
    sex_na = sum(is.na(Sex)),
    time_coverage_na = sum(is.na(TimeCoverage)),
    type_of_skill_na = sum(is.na(`Type of skill`)),
    footnote_na = sum(is.na(FootNote))
  )


## What is a more efficient way to find missing value for data_clmv all at once?
data_clmv %>%
  summarize_all(~ sum(is.na(.)))

```


## Outliers

In this section, we'll examine the data to see if there are any outliers. We'll start by creating our own data frame to build an intuition.

We'll use the aforementioned `summary()` function to explore the distribution of the data and how the outlier influences it.

We'll also create our first visualization for the purpose of understanding outliers. You can see that an outlier will not only distort the 'mean' or average value, but also distort any visualization, including the boxplot. 

```{r, include=FALSE}

# Create two vectors: one has an outlier
# these two vectors are identical except for one value
sample_data <- c(3,4,7,2,8,10,7,4,5,6,12,15,11,8,5,9,13,500)
sample_data_1 <- c(3,4,7,2,8,10,7,4,5,6,12,15,11,8,5,9,13,10)

# Convert two vectors into a tibble 
# note: Vectors are simply one-column tibbles
sample_data <- as.tibble(sample_data)
sample_data_1 <- as.tibble(sample_data_1)

# Use summary() function to see outliers in action
# Notice how 'sensitive' the mean/average is to outliers
summary(sample_data)
summary(sample_data_1)

# Quick Boxplot

# Note the 'median' line, 1st Quartile, 3rd Quartile, 
# Note the whiskers
sample_data_1 %>% 
  ggplot(aes(x = value)) +
  geom_boxplot()

# Boxplot with outlier
sample_data %>% 
  ggplot(aes(x = value)) +
  geom_boxplot()

```

## YOUR TURN: Outliers

```{r,include=FALSE}

# Create two vectors: one has an outlier
# these two vectors are identical except for one value - - UNCOMMENT to find out.

# inclass_sample_data <- c(3,4,7,2,8,10,7,4,5,6,12,15,11,8,5,9,13,10)
# inclass_sample_data_1 <- c(3,4,7,2,8,10,7,4,5,6,12,15,11,8,5,9,13,50000)

# Convert two vectors into a tibble 
# note: Vectors are simply one-column tibbles

# use as.tibble()

# use summary()

# Draw TWO Boxplots for...

# inclass_sample_data
# inclass_sample_data_1

```


## Outliers Continue

In this section, we'll explore outliers in the actual data. We'll select four columns: GeoAreaCode, TimePeriod, Value, Time_Detail and explore each column for details. 

```{r, include=FALSE}

# Outliers: Individual Histograms
# primarily num/dbl
# select only num / dbl
data %>%
    select(GeoAreaCode, TimePeriod, Value, Time_Detail) %>%  
  
    # note: I selected two variables that are strings/chr
    # they can still have outliers, but are slightly harder to detect
  
    # use mutate to change character to numeric
    mutate(
        Value = as.numeric(Value),
        Time_Detail = as.numeric(Time_Detail)
    ) %>%
    # use histogram one-by-one
    ggplot(aes(x = Time_Detail)) + 
    geom_histogram(bins = 30)

# Value

# NOTE: this data set looks at:
# Proportion (%) of youth and adults with ICT skills
# Percentages should not exceed 100%

data %>%
    select(GeoAreaCode, TimePeriod, Value, Time_Detail) %>%  
    
    mutate(
        Value = as.numeric(Value),
        Time_Detail = as.numeric(Time_Detail)
    ) %>%
    ggplot(aes(x = Value)) + 
    geom_histogram(bins = 30)


# Time Period
# You wouldn't expect to see an odd year like 3037 or 4059
data %>%
    select(GeoAreaCode, TimePeriod, Value, Time_Detail) %>%  
    mutate(
        Value = as.numeric(Value),
        Time_Detail = as.numeric(Time_Detail)
    ) %>%
    ggplot(aes(x = TimePeriod)) + 
    geom_histogram(bins = 30)

# GeoAreaCode
data %>%
    select(GeoAreaCode, TimePeriod, Value, Time_Detail) %>%  
    mutate(
        Value = as.numeric(Value),
        Time_Detail = as.numeric(Time_Detail)
    ) %>%
    ggplot(aes(x = GeoAreaCode)) + 
    geom_histogram(bins = 30)

# How can we display multiple boxplots?
library(reshape2)



# Select() only the day we're interested in
# Use mutate() to change character data types to numeric - just like above
multiple_histo <- data %>%
    select(GeoAreaCode, TimePeriod, Value, Time_Detail) %>%
    mutate(
        Value = as.numeric(Value),
        Time_Detail = as.numeric(Time_Detail)
    )

# NOTE: multiple_histo has four columns

# use melt() function from reshape2 package to turn from wide into long format
# now melt_multiple_histo has two columns
melt_multiple_histo <- melt(multiple_histo)

# plot with faceted boxplots to see four boxplots at the same time
# note: we need to have some awareness of the data dictionary
ggplot(data = melt_multiple_histo, mapping = aes(x = variable, y = value)) +
    geom_boxplot() +
    facet_wrap(~variable, scales = 'free')
```

## YOUR TURN: Outliers Continue

```{r,include=FALSE}

# start with data_clmv
# select GeoAreaCode, TimePeriod, Value (num / dbl)
# use mutate to change character to numeric 
# use histogram to plot each variable - GeoAreaCode, TimePeriod, value - one-by-one
# save to new variable called 'multiple_histo_clmv'

# use melt() function from reshape2 package to turn from wide into long format
# save to new variable called 'melt_multiple_histo_clmv'

# using 'melt_multiple_histo_clmv', plot with faceted boxplots to see four boxplots at the same time

```

## Compare Countries on their Performance with SDG Goal 4, Target 4.4

Finally, we'll use what we learn to begin exploring the actual SDG data. We'll use the boxplot to explore average proportions of children and adults with ICT skills, across different countries.

We'll draw our attention to how data must be pre-processed before we can visualize it. 

To keep it manageable, we'll use the `head()` function to only pick the first six countries (i.e., Algeria, Andorra, Austria, Azerbaijan, Bahrain and Belarus).

```{r, include=FALSE}
# Manipulating Columns and Rows ----

# caveat - this might not make sense
data %>%
    # we could just select GeoAreaName and Value
    select(SeriesDescription, GeoAreaName, Value) %>%
    # need to turn Value into numeric - like above
    mutate(Value = as.numeric(Value)) %>%
    # group_by GeoAreaName
    group_by(GeoAreaName) %>%
    summarize(avg_value = mean(Value)) %>%
    ungroup() %>%
    
    # keep it manageable (6 countries)
    head() %>%
    
# Plot: Boxplot
    ggplot(aes(x = GeoAreaName, y = avg_value)) +
    geom_boxplot() +
    facet_wrap(~ GeoAreaName, scales = 'free')
```

## YOUR TURN: Compare CLMV on their Performance with SDG Goal 4, Target 4.4

```{r, include=FALSE}
# Don't forget to use %>% at the end of each line

# start with data_clmv
# select GeoAreaName, Value (num / dbl)
# use mutate to change Value from character to numeric 
# group_by GeoAreaName
# use summarize() to find avg_value
# ungroup

# ggplot(aes(x = GeoAreaName, y = avg_value)) +
# geom_boxplot() +
# facet_wrap(~ GeoAreaName, scales = 'free')
```
