---
title: "Data_Wrangling"
author: "Paul Apivat Hanvongse"
date: "8/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup: Review

We covered a fair amount last time, we'll re-run some code to get setup:

```{r, include=FALSE}
# Take note of our software environment
sessionInfo()

# Load Libraries & Packages
install.packages("tidyverse")
install.packages("readxl")
library(tidyverse)
library(readxl)

# Read Data, Assign to Data Object
# YOU WILL NEED TO CHANGE THE PATH FOR YOUR LAPTOP

# recommended
data <- read_xlsx("./data/sdg_goal_4.4.xlsx")

#data <- read_xlsx("./data/sdg_goal_4.4.xlsx")
glimpse(data)




# YOU WILL NEED TO CHANGE THE PATH FOR YOUR LAPTOP
data_clmv <- 


```


## Data Wrangling: Selecting

DATA WRANGLING DEFINITION: Having explored our data, we're now ready to wrangle our data. [Data wrangling](https://en.wikipedia.org/wiki/Data_wrangling), similar to wrestling, is doing various operations **to** the data to answer questions we have about the data. Also called 'data munging', it's a transformation process to set the data up for further use, like analytics reporting and dashboarding, as one example. 

```{r,include=FALSE}

# Select columns you're interested in
data %>%
    select(GeoAreaName, 
           Value, 
           Units, 
           Sex, 
           `Type of skill`, 
           TimePeriod, 
           Time_Detail) 

# Select a range of columns
data %>%
    select(GeoAreaName:Value)


# De-select (or select "out") columns you don't want
data %>%
    select(-TimeCoverage, 
           -UpperBound, 
           -LowerBound, 
           -BasePeriod, 
           -GeoInfoUrl, 
           -FootNote, 
           -Nature) 

# Arrange columns with select()
data %>%
    # use everything() function
    select(TimePeriod, Sex, Value, everything()) 

# Different functions to use within select()
data %>%
    select(starts_with("g"))

data %>%
    select(contains("time"))

data %>%
    select(ends_with("period"))



# Piping into exploratory functions after selecting
data %>%
    select(GeoAreaName:Value) %>%
    view()


```

## YOUR TURN: Repeat the above with data_clmv

```{r,include=FALSE}

data_clmv 

```


## Data Wrangling: Mutate

We were not able to see `Value` - why? What can we do? Oftentime, we'll need to change the **data type** of a variable.


```{r, include=FALSE}

# Mutate allows us to change the variable type within a piping operation
# Note the data-type for 'Value' before and after running the mutate function
data %>%
    select(GeoAreaName, Value, Units, Sex, `Type of skill`, TimePeriod) %>%
    mutate(
        Value = as.numeric(Value)
    )



# TIP: Get into habit of looking up functions in the documentation
# Run the below code:

?as.numeric

```


## Data Wrangling: Subsetting through filter()

Now that we've examined potential outliers (and found none), we might want to **subset** our data to make our work (i.e., exploring/analyzing/visualizing) more *manageable*. 

We can begin asking specific questions of our data. What if we wanted to find proportion of Youth/Adult with ICT skills by Country & Gender?

We'll quickly find that we need more specific questions with `filter()`


```{r,include=FALSE}

# Use filter to sub-set your data and answer specific questions?
# What is the proportion of Gender & ICT Skills for Thailand in 2018?

data %>%
    # select specific columns (de-select others)
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    # rename column
    rename(type_of_skill = `Type of skill`) %>%
    # mutate
    mutate(
        Value = as.double(Value)
    ) %>%
     # filter on condition within parentheses
    filter(GeoAreaName == 'Thailand') %>% 
    filter(TimePeriod == 2018) %>% 
    arrange(desc(Value))


# Filter for MULTIPLE VALUES (e.g., Thailand and Cambodia)
data %>%
    filter(GeoAreaName %in% c('Thailand', 'Cambodia')) %>% 
    view()

# REVERSE CONDITIONAL LOGIC with filter

data %>%
    filter(!GeoAreaName %in% c('Thailand', 'Cambodia')) %>% 
    view()

data %>%
    filter(!Sex=='BOTHSEX')


# NOTE: See Indicator 4.4.1 data dictionary to understand ICT Sub-skills. 
```

## YOUR TURN: Watch short video clip on ICT sub-skills within Indicator 4.4.1

Then use filter to find the proportion of Gender & ICT Skills for Cambodia in 2017.

```{r,include=FALSE}

# Find proportion of Gender & ICT SKills for Cambodia in 2017.

data_clmv %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    # UNCOMMENT: filter(GeoAreaName == 'Cambodia') %>% 
    # UNCOMMENT: filter(TimePeriod == 2017) %>% 
    arrange(desc(Value))


#NOTE: Uncomment means to "delete" the hashtag (#) so the line turns into executable code

# What gender and type_of_skill had the highest percentage in 2017?

```


## Data Wrangling: Aggregate data by using group_by(), summarize(), arrange()

Previously, by filtering for GeoAreaName ("Thailand") and TimePeriod ("2018"), we saw detailed ranking of proportion of population with sub-types of ICT Skill and gender. Perhaps we want to step back and look at data in the **aggregate**.


```{r,include=FALSE}

# What if we aggregate across Gender (Male, Female, Bothsex), we want to look at the aggregate proportion by ICT Skills, for Thailand in 2018?

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    # filter on condition within parentheses
    # allowing to answer specific questions
    filter(GeoAreaName == 'Thailand') %>% 
    filter(TimePeriod == 2018) %>% 
    # group operations: look at mean_value of type_of_skill, across things **not** in the group_by()
    # - aggregate across Sex (try adding it)
    group_by(type_of_skill) %>%
    # When aggregating across Gender within a Year, we can use the mean_value (OR median_value)
    summarize(
        mean_value = mean(Value),
        median_value = median(Value)
    ) %>%
    ungroup() %>%
    # arrange mean_value in descending order
    arrange(desc(mean_value))

# NOTE: we see that more of the population does COPA, followed by CMFL, PCPR trailing. 
```

## YOUR TURN: Aggregate data by using group_by(), summarize() and arrange()

Here, we'll look at the average population percentage by type_of_skill.

```{r,include=FALSE}

# Aggregate across Gender (Male, Female, Bothsex), we want to look at the aggregate proportion by ICT Skills, for Cambodia in 2017?

data_clmv %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    filter(GeoAreaName == 'Cambodia') %>% 
    filter(TimePeriod == 2017) %>% 
    #group_by(type_of_skill) %>%
    #summarize(mean_value = mean(Value)) %>%
    #ungroup() %>%
    arrange(desc(mean_value))




## Run the following code to look at Documentation

?summary
?summarize
?summarise

```

## Data Wrangling: Does Order matter?

```{r,include=FALSE}

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    filter(GeoAreaName == 'Thailand') %>% 
    filter(TimePeriod == 2018) %>% 
    group_by(type_of_skill) %>%
    summarize(
        mean_value = mean(Value),
        median_value = median(Value)
    ) %>%
    ungroup() %>%
    arrange(desc(mean_value))

# switch up order 1

data %>%
    filter(GeoAreaName == 'Thailand') %>% 
    filter(TimePeriod == 2018) %>% 
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    # putting filter before rename, mutate is fine
    #filter(GeoAreaName == 'Thailand') %>% 
    #filter(TimePeriod == 2018) %>% 
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    group_by(type_of_skill) %>%
    summarize(
        mean_value = mean(Value),
        median_value = median(Value)
    ) %>%
    ungroup() %>%
    arrange(desc(mean_value))


# switch up order 2

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    filter(GeoAreaName == 'Thailand') %>% 
    filter(TimePeriod == 2018) %>% 
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    group_by(type_of_skill) %>%
    summarize(
        mean_value = mean(Value),
        median_value = median(Value)
    ) %>%
    ungroup() %>%
    arrange(desc(mean_value))

# switch up order 3: using result of rename() or mutate() functions

data %>%
    filter(GeoAreaName == 'Thailand') %>% 
    filter(TimePeriod == 2018) %>% 
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    #filter(Value < 10) %>%
    group_by(type_of_skill) %>%
    summarize(
        mean_value = mean(Value),
        median_value = median(Value)
    ) %>%
    ungroup() %>%
    arrange(desc(mean_value)) %>%
    # filter(Value) doesn't work down here
    filter(Value < 10)


# switch up order 4
data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    relocate(Sex, Value, GeoAreaName) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    # filter was previously here
    group_by(type_of_skill) %>%
    summarize(
        mean_value = mean(Value),
        median_value = median(Value)
    ) %>%
    ungroup() %>%
    # moving filter down below group_by & summarize() does not work
    #filter(GeoAreaName == 'Thailand') %>% 
    #filter(TimePeriod == 2018) %>% 
    arrange(desc(mean_value))


```



## Data Wrangling: Questions we can ask from the data

We'll start with a broad perspective on the data. We can begin to see various 'specific' questions we can ask of the data.

Previously, we aggregated across Gender for a specific year ("2018"). What if we wanted to aggregate across years (2014 & 2018), 

```{r,include=FALSE}

# Broad Perspective
# A histogram of all countries, across all gender and sub-ICT Skill types
data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    ggplot(aes(x = Value)) +
    geom_histogram(bins = 30, color = 'white')
    

# Add group_by GeoAreaName
# Plot using GeoAreaName, ordered by mean_value
data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    group_by(GeoAreaName) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    ungroup() %>%
    ggplot(aes(x = reorder(GeoAreaName, mean_value), y = mean_value)) +
    geom_histogram(stat = 'identity') +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    coord_flip()

# NOTE: we can group_by Country, Gender, TimePeriod and/or Sub-Skill (ICT)


# What specific ICT Skills did the population of Thailand have in 2018?
data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
     # filter on condition within parentheses
    filter(GeoAreaName == 'Thailand') %>% 
    # We take OUT the TimePeriod filter for a specific year
    # But we'll add TimePeriod to group_by
    group_by(type_of_skill, Sex, TimePeriod) %>%
    # group_by(type_of_skill, TimePeriod) means aggregating across Sex
    summarize(
        sum_value = sum(Value)
        #mean_value = mean(Value)
    ) %>%
    ungroup() %>%
    # arrange first by sum_value
    # then also by TimePeriod (sorting by multiple columns)
    arrange(desc(sum_value)) %>%
    arrange(desc(TimePeriod))

# What if we wanted to sum across both years (2014 & 2018)
# Take out TimePeriod
# Change sum_value to mean_value
    

```

## YOUR TURN: What specific ICT Skills did the population of Cambodia have in 2017?



```{r,include=FALSE}

data_clmv %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    # rename column
    rename(type_of_skill = `Type of skill`) %>%
    # mutate creates new column
    mutate(
        Value = as.double(Value)
    ) %>%
    filter(GeoAreaName=='Cambodia') %>%
    #group_by(type_of_skill, Sex, TimePeriod) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    ungroup()

```

## More Specific Questions

First we looked at Thailand in 2018, across Gender. 

Follow up question, what are the proportion of women in Thailand with ICT skills?


```{r,include=FALSE}

data %>%
    # select specific columns (de-select others)
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    # rename column
    rename(type_of_skill = `Type of skill`) %>%
    # mutate creates new column
    mutate(
        Value = as.double(Value)
    ) %>%
    filter(GeoAreaName == 'Thailand') %>% 
    filter(Sex=='FEMALE') %>%
    arrange(desc(Value)) 

# NOTE: When adding filter(Sex=='FEMALE'), the TimePeriod shows only 2018
# Also examing filter(s) from the View() of data

```

## YOUR TURN: Even More Specific

Let's look at Cambodia in 2017, specifically focusing on WOMEN with various ICT skills.

```{r,include=FALSE}

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    #filter(GeoAreaName == 'Cambodia') %>% 
    #filter(Sex=='FEMALE') %>%
    filter(Sex=='FEMALE') %>%
    arrange(desc(Value)) 



```


## Zooming Out: Cross-Country Comparison

We'll now use the functions we've learned to zoom out and examine proportion of population with various ICT Skills **across** type_of_skill, gender and time; making these comparisons between countries.

```{r,include=FALSE}

data %>%
    # select specific columns (de-select others)
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    # rename column
    rename(type_of_skill = `Type of skill`) %>%
    # mutate creates new column
    mutate(
        Value = as.double(Value)
    ) %>%
    # instead of filtering, jump to group_by
    group_by(GeoAreaName) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    ungroup() %>%
    arrange(desc(mean_value))

# If we start at most macro-level across gender, type_of_skill and time. We'll only group_by(GeoAreaName).


```


## Specific cross-country questions:

The most important thing we can do as an analyst is to be able to pose questions of our data. Here are some specific questions we could ask:

```{r,include=FALSE}

# Which countries did the BEST for women acquiring ICT Skills in 2017 ?

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>% 
    mutate(
        Value = as.numeric(Value)
    ) %>%
    group_by(GeoAreaName, Sex, TimePeriod) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    arrange(desc(mean_value)) %>%
    filter(TimePeriod==2017) %>%
    filter(Sex=='FEMALE')

# How about women acquiring ICT Skills over the entire time period (2014 - 2019)?

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>% 
    mutate(
        Value = as.numeric(Value)
    ) %>%
    # to summarize over extended time period, remove TimePeriod from group_by
    group_by(GeoAreaName, Sex) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    arrange(desc(mean_value)) %>%
    filter(Sex=='FEMALE')

# Which countries did the best for men acquiring ICT Skills in 2016?

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>% 
    mutate(
        Value = as.numeric(Value)
    ) %>%
    group_by(GeoAreaName, Sex, TimePeriod) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    arrange(desc(mean_value)) %>%
    filter(TimePeriod==2016) %>%
    filter(Sex=='MALE')
    

# How about over the entire time period?

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>% 
    mutate(
        Value = as.numeric(Value)
    ) %>%
    group_by(GeoAreaName, Sex) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    arrange(desc(mean_value)) %>%
    filter(Sex=='MALE')



```

## YOUR TURN: More Specific Questions of the Data

```{r,include=FALSE}

# YOUR TURN: Which countries did the best for both sex in acquiring ICT Skills in 2015?

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>% 
    mutate(
        Value = as.numeric(Value)
    ) %>%
    group_by(GeoAreaName, Sex, TimePeriod) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    arrange(desc(mean_value)) %>%
    #filter(TimePeriod==2015) %>%
    #filter(Sex=='BOTHSEX')
    
    
# How about over the entire time period?

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>% 
    mutate(
        Value = as.numeric(Value)
    ) %>%
    group_by(GeoAreaName, Sex) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    arrange(desc(mean_value)) %>%
    filter(Sex=='BOTHSEX')


# Which countries did the WORST for women acquiring ICT Skills in 2017 ?

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>% 
    mutate(
        Value = as.numeric(Value)
    ) %>%
    group_by(GeoAreaName, Sex, TimePeriod) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    #arrange(mean_value) %>%
    #filter(TimePeriod==2017) %>%
    #filter(Sex=='FEMALE')
    


# How about women acquiring ICT Skills over the entire time period (2014 - 2019)? Which countries did the WORST?

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>% 
    mutate(
        Value = as.numeric(Value)
    ) %>%
    # to summarize over extended time period, remove TimePeriod from group_by
    group_by(GeoAreaName, Sex) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    arrange(mean_value) %>%
    filter(Sex=='FEMALE')

# Which countries did the WORST for men acquiring ICT Skills in 2016?

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>% 
    mutate(
        Value = as.numeric(Value)
    ) %>%
    group_by(GeoAreaName, Sex, TimePeriod) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    arrange(desc(mean_value)) %>%
    #filter(TimePeriod==2016) %>%
    #filter(Sex=='MALE') %>%
    arrange(mean_value)


```

## Asking Specific Question: Specific ICT Skills Breakdown

```{r,include=FALSE}

# Which countries, across time, did the best (% of population) for EMAIL specifically?

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>% 
    mutate(
        Value = as.numeric(Value)
    ) %>%
    group_by(GeoAreaName) %>%
    filter(type_of_skill=='EMAIL') %>%
    arrange(desc(Value)) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    arrange(desc(mean_value))

# Which countries, across time, did the BEST (% of population) for PCPR specifically? (programming)

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>% 
    mutate(
        Value = as.numeric(Value)
    ) %>%
    group_by(GeoAreaName) %>%
    filter(type_of_skill=='PCPR') %>%
    arrange(desc(Value)) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    arrange(desc(mean_value))


# Which countries did the WORST?

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>% 
    mutate(
        Value = as.numeric(Value)
    ) %>%
    group_by(GeoAreaName) %>%
    filter(type_of_skill=='PCPR') %>%
    arrange(desc(Value)) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    #arrange(mean_value)


```


## What is an acceptable level for indicator 4.4.1?

```{r,include=FALSE}

## Country mean_values at 25th, 50th and 75th percentile ##

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod, Units) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(Value = as.numeric(Value)) %>%
    group_by(GeoAreaName) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    ungroup() %>%
    mutate(
        min_mean = min(mean_value),
        iqr_25_percentile = quantile(mean_value, probs = c(0.25)),
        iqr_50_percentile = quantile(mean_value, probs = c(0.50)),
        iqr_75_percentile = quantile(mean_value, probs = c(0.75)),
        max_mean = max(mean_value)
    ) %>%
    arrange(desc(mean_value)) %>%
    view()



?quantile  

## Binning Method
data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod, Units) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(Value = as.numeric(Value)) %>%
    group_by(GeoAreaName) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    ungroup() %>%
    mutate(
        mean_value_binned = ntile(mean_value, 5)
    ) %>%
    arrange(desc(mean_value)) %>%
    view()
 
## Using purrr
library(purrr)
    
p <- c(0.25, 0.50, 0.75)

p_names <- map_chr(p, ~paste0(.x*100, "%"))

p_funs <- map(p, ~partial(quantile, probs = .x, na.rm = TRUE)) %>%
    set_names(nm = p_names)

p_funs

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod, Units) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(Value = as.numeric(Value)) %>%
    group_by(GeoAreaName) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    summarize_at(vars(mean_value), funs(!!!p_funs))



```


## TIDY DATA PRINCIPLE: Pivot_Wider

What if we wanted each of the sub-skills to have their own columns, so we could compare GeoAreaName, TimePeriod and Sex for each of the sub-skills?

```{r,include=FALSE}


# PIVOT_WIDER - even better than Spread
# Examine by Sub-ICT-Skill
data %>%
    #filter(GeoAreaName=="Morocco" | GeoAreaName=="Qatar") %>% 
    select(GeoAreaName, TimePeriod, Sex, `Type of skill`, Value) %>%
    #group_by(GeoAreaName, TimePeriod, Sex, `Type of skill`, Value) %>%
    #ungroup() %>%
    pivot_wider(names_from = `Type of skill`, values_from = Value) %>% view()

# Examine by Time
data %>%
    select(GeoAreaName, TimePeriod, Sex, `Type of skill`, Value) %>%
    mutate(Value = as.numeric(Value)) %>%
    #group_by(GeoAreaName, TimePeriod, Sex, `Type of skill`, Value) %>%
    pivot_wider(names_from = TimePeriod, values_from = Value) %>% view()

```
