---
title: "Data_Wrangling"
author: "Paul Apivat Hanvongse"
date: "8/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup: Review

We covered a fair amount last time, we'll re-run some code to get setup:

```{r, include=FALSE}
# Take note of our software environment
sessionInfo()

# Load Libraries & Packages
library(tidyverse)
library(readxl)

# Read Data, Assign to Data Object
data <- read_xlsx("./data/sdg_goal_4.4.xlsx")
glimpse(data)

# Use another function, similar to glimpse() to explore

# Your Turn: Read data, assign to data_clmv
# use read_xlsx() function
data_clmv <- 


```


## Data Wrangling: Selecting

DATA WRANGLING DEFINITION: Having explored our data, we're now ready to wrangle our data. [Data wrangling](https://en.wikipedia.org/wiki/Data_wrangling), similar to wrestling, is doing various operations **to** the data to answer questions we have about the data. Also called 'data munging', it's a transformation process to set the data up for further use, like analytics reporting and dashboarding, as one example. 

```{r,include=FALSE}

# Select columns you're interested in
data %>%
    select(GeoAreaName, 
           Value, 
           Units, 
           Sex, 
           `Type of skill`, 
           TimePeriod, 
           Time_Detail) 

# Select a range of columns
data %>%
    select(GeoAreaName:Value)


# De-select (or select "out") columns you don't want
data %>%
    select(-TimeCoverage, 
           -UpperBound, 
           -LowerBound, 
           -BasePeriod, 
           -GeoInfoUrl, 
           -FootNote, 
           -Nature) 

# Arrange columns with select()
data %>%
    # use everything() function
    select(Sex, Value, everything()) 

# Different functions to use within select()
data %>%
    select(starts_with("g"))

data %>%
    select(contains("time"))

data %>%
    select(ends_with("period"))



# Piping into exploratory functions after selecting
data %>%
    select(GeoAreaName:Value) %>%
    str()


```

## YOUR TURN: Repeat the above with data_clmv

```{r,include=FALSE}

data_clmv 

```


## Data Wrangling: Mutate

We were not able to see `Value` - why? What can we do? Oftentime, we'll need to change the **data type** of a variable.


```{r, include=FALSE}

# Mutate allows us to change the variable type within a piping operation
# Note the data-type for 'Value' before and after running the mutate function
data %>%
    select(GeoAreaName, Value, Units, Sex, `Type of skill`, TimePeriod) %>%
    mutate(
        Value = as.numeric(Value)
    )



```


## Data Wrangling: Subsetting through filter()

Now that we've examined potential outliers (and found none), we might want to **subset** our data to make our work (i.e., exploring/analyzing/visualizing) more *manageable*. 

We can begin asking specific questions of our data. What if we wanted to find proportion of Youth/Adult with ICT skills by Country & Gender?

We'll quickly find that we need more specific questions with `filter()`


```{r,include=FALSE}

# Use filter to sub-set your data and answer specific questions?
# What is the proportion of Gender & ICT Skills for Thailand in 2018?

data %>%
    # select specific columns (de-select others)
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    # rename column
    rename(type_of_skill = `Type of skill`) %>%
    # mutate
    mutate(
        Value = as.double(Value)
    ) %>%
     # filter on condition within parentheses
    filter(GeoAreaName == 'Thailand') %>% 
    filter(TimePeriod == 2018) %>% 
    arrange(desc(Value))


# Filter for MULTIPLE VALUES (e.g., Thailand and Cambodia)
data %>%
    filter(GeoAreaName %in% c('Thailand', 'Cambodia')) %>% view()

# REVERSE CONDITIONAL LOGIC with filter

data %>%
    filter(!GeoAreaName %in% c('Thailand', 'Cambodia')) %>% view()

data %>%
    filter(!Sex=='BOTHSEX')


# NOTE: See Indicator 4.4.1 data dictionary to understand ICT Sub-skills. 
```

## YOUR TURN: Watch short video clip on ICT sub-skills within Indicator 4.4.1

Then use filter to find the proportion of Gender & ICT Skills for Cambodia in 2017.

```{r,include=FALSE}

# Find proportion of Gender & ICT SKills for Cambodia in 2017.

data_clmv %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    # UNCOMMENT: filter(GeoAreaName == 'Cambodia') %>% 
    # UNCOMMENT: filter(TimePeriod == 2017) %>% 
    arrange(desc(Value))

# What gender and type_of_skill had the highest percentage in 2017?

```


## Data Wrangling: Aggregate data by using group_by(), summarize(), arrange()

Previously, by filtering for GeoAreaName ("Thailand") and TimePeriod ("2018"), we saw detailed ranking of proportion of population with sub-types of ICT Skill and gender. Perhaps we want to step back and look at data in the **aggregate**.


```{r,include=FALSE}

# What if we aggregate across Gender (Male, Female, Bothsex), we want to look at the aggregate proportion by ICT Skills, for Thailand in 2018?

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    # filter on condition within parentheses
    # allowing to answer specific questions
    filter(GeoAreaName == 'Thailand') %>% 
    filter(TimePeriod == 2018) %>% 
    # group operations: look at mean_value of type_of_skill, across things **not** in the group_by()
    # - aggregate across Sex (try adding it)
    group_by(type_of_skill) %>%
    # When aggregating across Gender within a Year, we can use the mean_value (OR median_value)
    summarize(
        mean_value = mean(Value),
        median_value = median(Value)
    ) %>%
    ungroup() %>%
    # arrange mean_value in descending order
    arrange(desc(mean_value))

# NOTE: we see that more of the population does COPA, followed by CMFL, PCPR trailing. 
```

## YOUR TURN: Aggregate data by using group_by(), summarize() and arrange()

Here, we'll look at the average population percentage by type_of_skill.

```{r,include=FALSE}

# Aggregate across Gender (Male, Female, Bothsex), we want to look at the aggregate proportion by ICT Skills, for Cambodia in 2017?

data_clmv %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    filter(GeoAreaName == 'Cambodia') %>% 
    filter(TimePeriod == 2017) %>% 
    #group_by(type_of_skill) %>%
    #summarize(mean_value = mean(Value)) %>%
    #ungroup() %>%
    arrange(desc(mean_value))




## Run the following code to look at Documentation

?summary
?summarize
?summarise

```

## Data Wrangling: Does Order matter?

```{r,include=FALSE}

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    filter(GeoAreaName == 'Thailand') %>% 
    filter(TimePeriod == 2018) %>% 
    group_by(type_of_skill) %>%
    summarize(
        mean_value = mean(Value),
        median_value = median(Value)
    ) %>%
    ungroup() %>%
    arrange(desc(mean_value))

# switch up order 1

data %>%
    #filter(GeoAreaName == 'Thailand') %>% 
    #filter(TimePeriod == 2018) %>% 
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    # putting filter before rename, mutate is fine
    filter(GeoAreaName == 'Thailand') %>% 
    filter(TimePeriod == 2018) %>% 
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    group_by(type_of_skill) %>%
    summarize(
        mean_value = mean(Value),
        median_value = median(Value)
    ) %>%
    ungroup() %>%
    arrange(desc(mean_value))


# switch up order 2

data %>%
    filter(GeoAreaName == 'Thailand') %>% 
    filter(TimePeriod == 2018) %>% 
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    group_by(type_of_skill) %>%
    summarize(
        mean_value = mean(Value),
        median_value = median(Value)
    ) %>%
    ungroup() %>%
    arrange(desc(mean_value))

# switch up order 3: using result of rename() or mutate() functions

data %>%
    filter(GeoAreaName == 'Thailand') %>% 
    filter(TimePeriod == 2018) %>% 
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    #filter(Value < 10) %>%
    group_by(type_of_skill) %>%
    summarize(
        mean_value = mean(Value),
        median_value = median(Value)
    ) %>%
    ungroup() %>%
    arrange(desc(mean_value)) %>%
    # filter(Value) doesn't work down here
    filter(Value < 10)


# switch up order 4
data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    relocate(Sex, Value, GeoAreaName) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    # filter was previously here
    group_by(type_of_skill) %>%
    summarize(
        mean_value = mean(Value),
        median_value = median(Value)
    ) %>%
    ungroup() %>%
    # moving filter down below group_by & summarize() does not work
    filter(GeoAreaName == 'Thailand') %>% 
    filter(TimePeriod == 2018) %>% 
    arrange(desc(mean_value))


```

## Data Wrangling: What should the order of operations be?

```{r,include=FALSE}

# The ordering of the functions should depend on your question:
data %>%
    filter(GeoAreaName == 'Thailand') %>% 
    filter(TimePeriod == 2018) %>% 
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    #filter(Value < 10) %>%
    group_by(type_of_skill) %>%
    summarize(
        mean_value = mean(Value),
        median_value = median(Value)
    ) %>%
    ungroup() %>%
    arrange(desc(mean_value)) %>%
    # filter(Value) doesn't work down here
    filter(Value < 10)
```

## Pick up here: Questions (PPT)

## Data Wrangling: Aggregating across TimePeriod

Previously, we aggregated across Gender for a specific year ("2018"). What if we wanted to aggregate across years (2014 & 2018), 

```{r,include=FALSE}

data %>%
    # select specific columns (de-select others)
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    # rename column
    rename(type_of_skill = `Type of skill`) %>%
    # mutate creates new column
    mutate(
        Value = as.double(Value)
    ) %>%
     # filter on condition within parentheses
    filter(GeoAreaName == 'Thailand') %>% 
    # We take OUT the TimePeriod filter for a specific year
    # But we'll add TimePeriod to group_by
    group_by(type_of_skill, TimePeriod) %>%
    # group_by(type_of_skill, TimePeriod) means aggregating across Sex
    summarize(
        sum_value = sum(Value),
        mean_value = mean(Value)
    ) %>%
    ungroup() %>%
    # arrange first by sum_value
    # then also by TimePeriod (sorting by multiple columns)
    arrange(desc(sum_value)) %>%
    arrange(desc(TimePeriod))

# What if we wanted to sum across both years (2014 & 2018)
# Take out TimePeriod
# Change sum_value to mean_value
    

```

## YOUR TURN: Aggregating Across Gender

Challenge: Since Cambodia's data is only available for 2017, can we aggregate across ICT Skill Types but for EACH gender? (Female, Male, Bothsex)?

Here we'll see the average percentage value for each Gender (across all ICT skill types)

```{r,include=FALSE}

data_clmv %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    # rename column
    rename(type_of_skill = `Type of skill`) %>%
    # mutate creates new column
    mutate(
        Value = as.double(Value)
    ) %>%
    filter(GeoAreaName=='Cambodia') %>%
    # your code here
    summarize(
        mean_value = mean(Value)
    ) %>%
    ungroup()


# HINT: group_by(Sex) %>%
```

## Even More Specific

First we looked at Thailand in 2018, across Gender. Now, what if we wanted to focus specifically on WOMEN with various ICT skills


```{r,include=FALSE}

data %>%
    # select specific columns (de-select others)
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    # rename column
    rename(type_of_skill = `Type of skill`) %>%
    # mutate creates new column
    mutate(
        Value = as.double(Value)
    ) %>%
     # filter on condition within parentheses
    filter(GeoAreaName == 'Thailand') %>% 
    # filter on gender
    filter(Sex=='FEMALE') %>%
    arrange(desc(Value)) 

# NOTE: When adding filter(Sex=='FEMALE'), the TimePeriod shows only 2018
# Also examing filter(s) from the View() of data

```

## YOUR TURN: Even More Specific

Let's look at Cambodia in 2017, specifically focusing on WOMEN with various ICT skills.

```{r,include=FALSE}

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    # your code here
    # your code here
    filter(Sex=='FEMALE') %>%
    arrange(desc(Value)) 


# HINT: filter(GeoAreaName == 'Cambodia') %>% 
# HINT: filter(Sex=='FEMALE') %>%

```


## Examining Data Across Countries

We'll now use the functions we've learned to zoom out and examine proportion of population with various ICT Skills **across** type_of_skill, gender and time; making these comparisons between countries.

```{r,include=FALSE}

data %>%
    # select specific columns (de-select others)
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    # rename column
    rename(type_of_skill = `Type of skill`) %>%
    # mutate creates new column
    mutate(
        Value = as.double(Value)
    ) %>%
    # instead of filtering, jump to group_by
    group_by(GeoAreaName) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    ungroup() %>%
    arrange(desc(mean_value))

# If we start at most macro-level across gender, type_of_skill and time. We'll only group_by(GeoAreaName).


```

## YOUR TURN: Make a cross-country comparison for Thailand and Cambodia

```{r,include=FALSE}

```

## Asking Specific Questions of the Data

The most important thing we can do as an analyst is to be able to pose questions of our data. Here are some specific questions we could ask:

```{r,include=FALSE}

# Which countries did the BEST for women acquiring ICT Skills in 2017 ?

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>% 
    mutate(
        Value = as.numeric(Value)
    ) %>%
    group_by(GeoAreaName, Sex, TimePeriod) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    arrange(desc(mean_value)) %>%
    filter(TimePeriod==2017) %>%
    filter(Sex=='FEMALE')

# How about women acquiring ICT Skills over the entire time period (2014 - 2019)?

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>% 
    mutate(
        Value = as.numeric(Value)
    ) %>%
    # to summarize over extended time period, remove TimePeriod from group_by
    group_by(GeoAreaName, Sex) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    arrange(desc(mean_value)) %>%
    filter(Sex=='FEMALE')

# YOUR TURN: Which countries did the best for men acquiring ICT Skills in 2016?

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>% 
    mutate(
        Value = as.numeric(Value)
    ) %>%
    group_by(GeoAreaName, Sex, TimePeriod) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    arrange(desc(mean_value)) %>%
    # your code here
    
    
    
# HINT: filter(TimePeriod==2016) %>%
# HINT: filter(Sex=='MALE')

# How about over the entire time period?

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>% 
    mutate(
        Value = as.numeric(Value)
    ) %>%
    group_by(GeoAreaName, Sex) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    arrange(desc(mean_value)) %>%
    filter(Sex=='MALE')

# YOUR TURN: Which countries did the best for both sex in acquiring ICT Skills in 2015?

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>% 
    mutate(
        Value = as.numeric(Value)
    ) %>%
    group_by(GeoAreaName, Sex, TimePeriod) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    arrange(desc(mean_value)) %>%
    # your code here
    # your code here
    
    
# HINT: filter(TimePeriod==2015) %>%
# HINT: filter(Sex=='BOTHSEX')

# How about over the entire time period?

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>% 
    mutate(
        Value = as.numeric(Value)
    ) %>%
    group_by(GeoAreaName, Sex) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    arrange(desc(mean_value)) %>%
    filter(Sex=='BOTHSEX')

```

## YOUR TURN: More Specific Questions of the Data

```{r,include=FALSE}

# Which countries did the WORST for women acquiring ICT Skills in 2017 ?

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>% 
    mutate(
        Value = as.numeric(Value)
    ) %>%
    group_by(GeoAreaName, Sex, TimePeriod) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    # your code here
    



# HINT: arrange(mean_value) %>%
# HINT: filter(TimePeriod==2017) %>%
# HINT: filter(Sex=='FEMALE')

# How about women acquiring ICT Skills over the entire time period (2014 - 2019)? Which countries did the WORST?

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>% 
    mutate(
        Value = as.numeric(Value)
    ) %>%
    # to summarize over extended time period, remove TimePeriod from group_by
    group_by(GeoAreaName, Sex) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    arrange(mean_value) %>%
    filter(Sex=='FEMALE')

# Which countries did the WORST for men acquiring ICT Skills in 2016?

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>% 
    mutate(
        Value = as.numeric(Value)
    ) %>%
    group_by(GeoAreaName, Sex, TimePeriod) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    arrange(desc(mean_value)) %>%
    filter(TimePeriod==2016) %>%
    filter(Sex=='MALE') %>%
    arrange(mean_value)


# How about over the entire time period (2014 - 2019)? Which countries did the WORST for men?

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>% 
    mutate(
        Value = as.numeric(Value)
    ) %>%
    group_by(GeoAreaName, Sex) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    arrange(desc(mean_value)) %>%
    filter(Sex=='MALE') %>%
    arrange(mean_value)
```

## Asking Specific Question: Specific ICT Skills Breakdown

```{r,include=FALSE}

# Which countries, across time, did the best (% of population) for EMAIL specifically?

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>% 
    mutate(
        Value = as.numeric(Value)
    ) %>%
    group_by(GeoAreaName) %>%
    filter(type_of_skill=='EMAIL') %>%
    arrange(desc(Value)) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    arrange(desc(mean_value))


# Which countries had the most "TimePeriod"(s) recorded? (As in tally)

data %>%
    select(GeoAreaName, TimePeriod) %>%
    group_by(GeoAreaName, TimePeriod) %>%
    tally(sort = TRUE) %>%
    summarize(
        sum_n = sum(n)
    ) %>%
    arrange(desc(sum_n))

```

## YOUR TURN: asking Specific Question: Specific ICT Skills Breakdown

```{r,include=FALSE}


# Which countries, across time, did the BEST (% of population) for PCPR specifically? (programming)

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>% 
    mutate(
        Value = as.numeric(Value)
    ) %>%
    group_by(GeoAreaName) %>%
    # your code here
    arrange(desc(Value)) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    arrange(desc(mean_value))


# HINT: filter(type_of_skill=='PCPR') %>%


# Which countries did the WORST?

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>% 
    mutate(
        Value = as.numeric(Value)
    ) %>%
    group_by(GeoAreaName) %>%
    filter(type_of_skill=='PCPR') %>%
    arrange(desc(Value)) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    # your code here


# HINT: arrange(mean_value)

```

## What is an acceptable level for indicator 4.4.1?

```{r,include=FALSE}

## Country mean_values at 25th, 50th and 75th percentile ##

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod, Units) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(Value = as.numeric(Value)) %>%
    group_by(GeoAreaName) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    mutate(
        min_mean = min(mean_value),
        iqr_25_percentile = quantile(mean_value, probs = c(0.25)),
        iqr_50_percentile = quantile(mean_value, probs = c(0.50)),
        iqr_75_percentile = quantile(mean_value, probs = c(0.75)),
        max_mean = max(mean_value)
    ) %>%
    arrange(desc(mean_value)) %>%
    view()
    

## Binning Method
data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod, Units) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(Value = as.numeric(Value)) %>%
    group_by(GeoAreaName) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    mutate(
        mean_value_binned = ntile(mean_value, 4)
    ) %>%
    arrange(desc(mean_value)) %>%
    view()
 
## Using purrr
library(purrr)
    
p <- c(0.25, 0.50, 0.75)

p_names <- map_chr(p, ~paste0(.x*100, "%"))

p_funs <- map(p, ~partial(quantile, probs = .x, na.rm = TRUE)) %>%
    set_names(nm = p_names)

p_funs

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod, Units) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(Value = as.numeric(Value)) %>%
    group_by(GeoAreaName) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    summarize_at(vars(mean_value), funs(!!!p_funs))



```


## TIDY DATA PRINCIPLE: Spread & Pivot_Wider

```{r,include=FALSE}

# SPREAD
# NOTE: not sure if this is the best place to introduce spread
data %>%
    filter(GeoAreaName=="Morocco" | GeoAreaName=="Qatar") %>% 
    select(GeoAreaName, TimePeriod, Sex, `Type of skill`, Value) %>%
    group_by(GeoAreaName, TimePeriod, Sex, `Type of skill`, Value) %>%
    # Error: Each row of output must be identified by a unique combination of keys.
    # rowid_to_column() address this error
    tibble::rowid_to_column() %>%
    spread(key = `Type of skill`, value = Value) %>% view()

# PIVOT_WIDER - even better than Spread
# Examine by Sub-ICT-Skill
data %>%
    filter(GeoAreaName=="Morocco" | GeoAreaName=="Qatar") %>% 
    select(GeoAreaName, TimePeriod, Sex, `Type of skill`, Value) %>%
    group_by(GeoAreaName, TimePeriod, Sex, `Type of skill`, Value) %>%
    pivot_wider(names_from = `Type of skill`, values_from = Value) %>% view()

# Examine by Time
data %>%
    select(GeoAreaName, TimePeriod, Sex, `Type of skill`, Value) %>%
    mutate(Value = as.numeric(Value)) %>%
    group_by(GeoAreaName, TimePeriod, Sex, `Type of skill`, Value) %>%
    pivot_wider(names_from = TimePeriod, values_from = Value) %>% view()

```
