---
title: "Data_Visualization.Rmd"
author: "Paul Apivat Hanvongse"
date: "9/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup

You know the drill.

```{r, include=FALSE}
# Take note of our software environment
sessionInfo()

# Load Libraries & Packages
install.packages("tidyverse")
install.packages("readxl")
library(tidyverse)
library(readxl)

# Read Data, Assign to Data Object
# YOU WILL NEED TO CHANGE THE PATH FOR YOUR LAPTOP

# recommended
data <- read_xlsx("./data/sdg_goal_4.4.xlsx")

#data <- read_xlsx("./data/sdg_goal_4.4.xlsx")
glimpse(data)


# YOU WILL NEED TO CHANGE THE PATH FOR YOUR LAPTOP
data_clmv <- read_xlsx("./data/sdg_goal_4.4_clmv.xlsx")


```

## Quick Review: Data Wrangling

A pre-requisite for data visualization is data wrangling.

```{r, include=FALSE}

# Group by Type of Skill, across GeoAreaName & TimePeriod
data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    # group by 'type_of_skill', summarize across GeoAreaName & TimePeriod
    group_by(type_of_skill) %>%
    summarize(
        mean_value = mean(Value),
        median_value = median(Value)
    ) %>%
    ungroup() %>%
    arrange(desc(mean_value))

# 88 distinct GeoAreaName
data %>%
    group_by(GeoAreaName) %>%
    summarize(distinct_countries = n_distinct(GeoAreaName))

# 9 distinct Type of Skill
data %>%
    group_by(`Type of skill`) %>%
    summarize(distinct_skill_type = n_distinct(`Type of skill`))9

data %>%
    group_by(Sex) %>%
    summarize(distinct_gender = n_distinct(Sex))

# Group by GeoAreaName & Type of Skill 
# Assuming there is Data Availability on 9 distinct skills for all 88 countries
# we should see ~792 observations
data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    group_by(GeoAreaName, type_of_skill) %>%
    summarize(
        mean_value = mean(Value),
        median_value = median(Value)
    ) %>%
    ungroup() %>%
    arrange(desc(mean_value))

# Group by Sex & Type of Skill
# Should see 27 rows (3 * 9)
data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    group_by(Sex, type_of_skill) %>%
    summarize(
        mean_value = mean(Value),
        median_value = median(Value)
    ) %>%
    ungroup() %>%
    arrange(desc(mean_value))


# Add filters for GeoAreaName, Sex, TimePeriod

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    filter(GeoAreaName == 'Thailand') %>% 
    filter(TimePeriod == 2018) %>% 
    filter(Sex=='FEMALE') %>%
    group_by(type_of_skill) %>%
    summarize(
        mean_value = mean(Value),
        median_value = median(Value)
    ) %>%
    ungroup() %>%
    arrange(desc(mean_value))
```

## Basic Visualizations: One Categorical Variable

```{r, include=FALSE}

# Bar Chart
data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    # group by 'type_of_skill', summarize across GeoAreaName & TimePeriod
    group_by(type_of_skill) %>%
    summarize(
        mean_value = mean(Value),
        median_value = median(Value)
    ) %>%
    ungroup() %>%
    arrange(desc(mean_value)) %>%
    
    # add Bar Chart
    ggplot(aes(x = type_of_skill, y = mean_value)) +
    geom_col()

# Pie Chart
data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    # group by 'type_of_skill', summarize across GeoAreaName & TimePeriod
    group_by(type_of_skill) %>%
    summarize(
        mean_value = mean(Value),
        median_value = median(Value)
    ) %>%
    ungroup() %>%
    arrange(desc(mean_value)) %>%
    ggplot(aes(x = "", y = mean_value, fill = type_of_skill)) +
    geom_bar(stat = 'identity', width = 1) +
    coord_polar("y", start = 0)

# Points 
data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    # group by 'type_of_skill', summarize across GeoAreaName & TimePeriod
    group_by(type_of_skill) %>%
    summarize(
        mean_value = mean(Value),
        median_value = median(Value)
    ) %>%
    ungroup() %>%
    arrange(desc(mean_value)) %>%
    ggplot(aes(x = type_of_skill, y = mean_value)) +
    geom_point(aes(color = type_of_skill), size = 8, alpha = 0.5)

# Lollipop plot = point + segment
data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    # group by 'type_of_skill', summarize across GeoAreaName & TimePeriod
    group_by(type_of_skill) %>%
    summarize(
        mean_value = mean(Value),
        median_value = median(Value)
    ) %>%
    ungroup() %>%
    arrange(desc(mean_value)) %>%
    ggplot(aes(x = type_of_skill, y = mean_value)) +
    geom_point(aes(color = type_of_skill), size = 8, alpha = 0.5) +
    # add segment
    geom_segment(aes(x=type_of_skill, xend=type_of_skill, y=0, yend=mean_value))

```

## YOUR TURN: Basic Visualizations - One Categorical Variable

You'll repeat the above, except you'll filter for *women in Thailand for the year 2018*

```{r,include=FALSE}

# Try on your own before looking at the hints:

# Bar chart
# Pie chart
# Points 
# Lollipops

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    filter(GeoAreaName == 'Thailand') %>% 
    filter(TimePeriod == 2018) %>% 
    filter(Sex=='FEMALE') %>%
    group_by(type_of_skill) %>%
    summarize(
        mean_value = mean(Value),
        median_value = median(Value)
    ) %>%
    ungroup() %>%
    arrange(desc(mean_value)) %>%
    # your code here




### Hints Below ###

# Bar chart
data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    filter(GeoAreaName == 'Thailand') %>% 
    filter(TimePeriod == 2018) %>% 
    filter(Sex=='FEMALE') %>%
    group_by(type_of_skill) %>%
    summarize(
        mean_value = mean(Value),
        median_value = median(Value)
    ) %>%
    ungroup() %>%
    arrange(desc(mean_value)) %>%
    # add Bar Chart
    #ggplot(aes(x = type_of_skill, y = mean_value)) +
    #geom_col()

# Pie Chart
data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    filter(GeoAreaName == 'Thailand') %>% 
    filter(TimePeriod == 2018) %>% 
    filter(Sex=='FEMALE') %>%
    group_by(type_of_skill) %>%
    summarize(
        mean_value = mean(Value),
        median_value = median(Value)
    ) %>%
    ungroup() %>%
    arrange(desc(mean_value)) %>%
    #ggplot(aes(x = "", y = mean_value, fill = type_of_skill)) +
    #geom_bar(stat = 'identity', width = 1) +
    #coord_polar("y", start = 0)

# Point
data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    filter(GeoAreaName == 'Thailand') %>% 
    filter(TimePeriod == 2018) %>% 
    filter(Sex=='FEMALE') %>%
    group_by(type_of_skill) %>%
    summarize(
        mean_value = mean(Value),
        median_value = median(Value)
    ) %>%
    ungroup() %>%
    arrange(desc(mean_value)) %>%
    #ggplot(aes(x = type_of_skill, y = mean_value)) +
    #geom_point(aes(color = type_of_skill), size = 8, alpha = 0.5)

# Lollipop
data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    filter(GeoAreaName == 'Thailand') %>% 
    filter(TimePeriod == 2018) %>% 
    filter(Sex=='FEMALE') %>%
    group_by(type_of_skill) %>%
    summarize(
        mean_value = mean(Value),
        median_value = median(Value)
    ) %>%
    ungroup() %>%
    arrange(desc(mean_value)) %>%
    #ggplot(aes(x = type_of_skill, y = mean_value)) +
    #geom_point(aes(color = type_of_skill), size = 8, alpha = 0.5) +
    # add segment
    #geom_segment(aes(x=type_of_skill, xend=type_of_skill, y=0, yend=mean_value))

```

## Extra Challenge: Additional Categorical Variables

Instead of Type of Skill, try visualizing when group_by(GeoAreaName)

```{r,include=FALSE}

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    group_by(GeoAreaName) %>%
    summarize(
        mean_value = mean(Value),
        median_value = median(Value)
    ) %>%
    ungroup() %>%
    arrange(desc(mean_value)) %>%
    # your code here
    
    
# HINT BELOW #
    
    #ggplot(aes(x = GeoAreaName, y = mean_value)) +
    #geom_col()
    
# More legible #
    
    #ggplot(aes(x = reorder(GeoAreaName, mean_value), y = mean_value)) +
    #geom_col() +
    #theme(axis.text.x = element_text(angle = 90, hjust = 1))
    

```


## Basic Visualization: One Numeric Variable

Instead of the categories (Type of Skill or GeoAreaName or Gender), we'll visualize the Value (a numeric variable).

```{r,include=FALSE}

# Histogram: Median Value
# (group by 'type of skill')
data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    # group by 'type_of_skill' 
    group_by(type_of_skill) %>%
    summarize(
        mean_value = mean(Value),
        median_value = median(Value)
    ) %>%
    ungroup() %>%
    arrange(desc(mean_value)) %>%
    ggplot(aes(x = median_value)) +
    geom_histogram()

# Histogram: Mean Value
# Group by Type of SKill AND GeoAreaName
data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    # group by GeoAreaName and 'type_of_skill' 
    group_by(GeoAreaName, type_of_skill) %>%
    summarize(
        mean_value = mean(Value),
        median_value = median(Value)
    ) %>%
    ungroup() %>%
    arrange(desc(mean_value)) %>%
    ggplot(aes(x = median_value)) +
    geom_histogram()

# Density Plot of Mean Value
# group by GeoAreaName and type of skill
data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    # group by GeoAreaName and 'type_of_skill' 
    group_by(GeoAreaName, type_of_skill) %>%
    summarize(
        mean_value = mean(Value),
        median_value = median(Value)
    ) %>%
    ungroup() %>%
    arrange(desc(mean_value)) %>%
    ggplot(aes(x = mean_value)) +
    geom_density(fill="#69b3a2", color="#e9ecef", alpha=0.8)

```

## One Numerical and One Categorical

```{r,include=FALSE}

# Two categoric variables
data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    # group by 'type_of_skill', summarize across GeoAreaName & TimePeriod
    group_by(GeoAreaName, type_of_skill) %>%
    summarize(
        mean_value = mean(Value),
        median_value = median(Value)
    ) %>%
    ungroup() %>%
    arrange(desc(mean_value)) %>%
    # Categorical variables: GeoAreaName & type_of_skill
    ggplot(aes(x=GeoAreaName, y=mean_value, color=type_of_skill)) +
    geom_point()


data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    # group by 'type_of_skill', summarize across GeoAreaName & TimePeriod
    group_by(Sex, type_of_skill) %>%
    summarize(
        mean_value = mean(Value),
        median_value = median(Value)
    ) %>%
    ungroup() %>%
    arrange(desc(mean_value)) %>%
    # Categorical variables: Sex & type_of_skill
    ggplot(aes(x=Sex, y=mean_value, color=type_of_skill)) +
    geom_point(size=6)


# Several observations per Group

# Observations will be Values across Gender/Time
# Group will be by countries

data %>%
    select(GeoAreaName, Value) %>%
    mutate(Value = as.numeric(Value)) %>%
    group_by(GeoAreaName) %>%
    summarize(avg_value = mean(Value)) %>%
    ungroup() %>%
    ggplot(aes(x = GeoAreaName, y = avg_value)) +
    geom_boxplot(aes(color = ifelse(avg_value > 40, 'green', 'red'))) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))

```


## Pivot Wider & Pivot Longer 

```{r,include=FALSE}

# PIVOT_WIDER - even better than Spread
# Examine by Sub-ICT-Skill
data %>%
    select(GeoAreaName, TimePeriod, Sex, `Type of skill`, Value) %>%
    group_by(GeoAreaName, TimePeriod, Sex, `Type of skill`, Value) %>%
    # Give each Type of skill its own column
    pivot_wider(names_from = `Type of skill`, values_from = Value) %>% view()


# Two Numeric Variables
install.packages('ggExtra')
library(ggExtra)

# RELATIONSHIPS #

# Basic Scatter Plot: COPA & EMAIL
# Basic Scatter Plot: COPA & PCPR
data %>%
    select(GeoAreaName, TimePeriod, Sex, `Type of skill`, Value) %>%
    group_by(GeoAreaName, TimePeriod, Sex, `Type of skill`, Value) %>%
    pivot_wider(names_from = `Type of skill`, values_from = Value) %>%
    mutate(
        COPA = as.numeric(COPA),
        EMAIL = as.numeric(EMAIL),
        PCPR = as.numeric(PCPR),
        INST = as.numeric(INST)
    ) %>%
    # Group by GeoAreaName, across TimePeriod, Sex
    group_by(GeoAreaName) %>%
    summarize(
        avg_COPA = mean(COPA),
        avg_EMAIL = mean(EMAIL),
        avg_PCPR = mean(PCPR),
        avg_INST = mean(INST)
    ) %>%
    ungroup() %>%
    ggplot(aes(x = avg_COPA, y = avg_PCPR)) + 
    geom_point()






# Basic Scatter Plot (color cluster by Gender)
p <- data %>%
    select(GeoAreaName, TimePeriod, Sex, `Type of skill`, Value) %>%
    group_by(GeoAreaName, TimePeriod, Sex, `Type of skill`, Value) %>%
    pivot_wider(names_from = `Type of skill`, values_from = Value) %>%
    mutate(
        COPA = as.numeric(COPA),
        EMAIL = as.numeric(EMAIL),
        PCPR = as.numeric(PCPR)
    ) %>%
    # Group by GeoAreaName, across TimePeriod, Sex
    group_by(GeoAreaName, Sex) %>%
    summarize(
        avg_COPA = mean(COPA, na.rm = TRUE),
        avg_EMAIL = mean(EMAIL, na.rm = TRUE),
        avg_PCPR = mean(PCPR, na.rm = TRUE)
    ) %>%
    ungroup() %>%
    ggplot(aes(x = avg_PCPR, y = avg_EMAIL, color = Sex)) + 
    geom_point()

# Scatter Plot with Marginal Distribution
ggMarginal(p, type = 'histogram')



```



## Visualization: Bells & Whistles

```{r,include=FALSE}

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>%
    mutate(
        Value = as.double(Value)
    ) %>%
    # group by 'type_of_skill', summarize across GeoAreaName & TimePeriod
    group_by(GeoAreaName, type_of_skill) %>%
    summarize(
        mean_value = mean(Value),
        median_value = median(Value)
    ) %>%
    ungroup() %>%
    arrange(desc(mean_value)) %>%
    # Categorical variables: GeoAreaName & type_of_skill
    ggplot(aes(x=GeoAreaName, y=mean_value, color=type_of_skill)) +
    geom_point()



# Numeric & Categoric
data %>%
    select(GeoAreaName, Value) %>%
    mutate(Value = as.numeric(Value)) %>%
    group_by(GeoAreaName) %>%
    summarize(avg_value = mean(Value)) %>%
    ungroup() %>%
    ggplot(aes(x = GeoAreaName, y = avg_value)) +
    geom_boxplot(aes(color = ifelse(avg_value > 40, 'green', 'red'))) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))

```


