---
title: "Data_Wrangling"
author: "Paul Apivat Hanvongse"
date: "8/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup: Review

We covered a fair amount last time, we'll re-run some code to get setup:

```{r, include=FALSE}
# Take note of our software environment
sessionInfo()

# Load Libraries & Packages
library(tidyverse)
library(readxl)

# Read Data, Assign to Data Object
data <- read_xlsx("./data/sdg_goal_4.4.xlsx")
glimpse(data)

# Use another function, similar to glimpse() to explore

# Your Turn: Read data, assign to data_clmv
# use read_xlsx() function
data_clmv <- 


```

## Review

We covered effficient ways to find all **missing values**. 

```{r, include=FALSE}
# What is a more efficient way to find missing value for data all at once?
data %>%
    summarize_all(~ sum(is.na(.))) 
    # Output results of this operation in spreadsheet view.

# What are the rows with missing data?

```

## Data Wrangling: Selecting

Having explored our data, we're now ready to wrangle our data. Data wrangling, similar to wrestling, is doing various operations **to** the data to answer questions we have about the data. 

```{r,include=FALSE}

# We saw all the columns with missing data
# De-select those columns with missing values, we will not use them in the subsequent analysis

data %>%
    select(-TimeCoverage, 
           -UpperBound, 
           -LowerBound, 
           -BasePeriod, 
           -GeoInfoUrl, 
           -FootNote, 
           -Nature) %>%
    view()

# Alternatively, Instead of de-select, select columns you're interested in
data %>%
    select(GeoAreaName, 
           Value, 
           Units, 
           Sex, 
           `Type of skill`, 
           TimePeriod, 
           Time_Detail) %>%
    view()

# What TYPE of variables have we selected? This gives us a clue as to how to proceed

data %>%
    select(GeoAreaName, Value, Units, Sex, `Type of skill`, TimePeriod, Time_Detail) %>%
    # also try summary()
    str()


# Note: through piping (%>%) we can combine new functions (select) with previous functions we learned (str)



```

## Data Wrangling: Mutate

We were not able to see `Value` - why? What can we do? Oftentime, we'll need to change the **data type** of a variable, similar to how we change **vectors** to **tibble / data frame**, BEFORE we could do any visualization operations.  

We'll note that even though we're in the exploration / wrangling phase, we'll use visualization to help us make sense of the data. 

Note the distinction between visualizing *for yourself* vs visualization *for others*. 


```{r, include=FALSE}
# Quick Review

# Atomic Vectors
# Try visualizing BEFORE turning into Tibble
inclass_sample_data <- c(3,4,7,2,8,10,7,4,5,6,12,15,11,8,5,9,13,10)
inclass_sample_data_1 <- c(3,4,7,2,8,10,7,4,5,6,12,15,11,8,5,9,13,50000)

# Vectors into Tibble
inclass_sample_data <- as.tibble(inclass_sample_data)
inclass_sample_data_1 <- as.tibble(inclass_sample_data_1)

# Intro to visualization (for detecting outliers)
inclass_sample_data %>%
    ggplot(aes(x = value)) +
    geom_boxplot()

# With outliers
inclass_sample_data_1 %>%
    ggplot(aes(x = value)) +
    geom_boxplot()

# Mutate allows us to change the variable type within a piping operation
# highlight before mutate to see Value data type before, then after
data %>%
    select(GeoAreaName, Value, Units, Sex, `Type of skill`, TimePeriod) %>%
    mutate(
        Value = as.numeric(Value)
    )

# Note: We took out Time_Detail, leaving only TimePeriod why? Try adding it back above to see.

# Examine Outliers within Data, in the Value column

data %>%
    select(GeoAreaName, Value, Units, Sex, `Type of skill`, TimePeriod) %>%
    mutate(
        Value = as.numeric(Value)
    ) %>%
    # quick way to get distribution of numerical variables
    summary()

# visually explore outliers in Value
# also try geom_histogram
data %>%
    select(GeoAreaName, Value, Units, Sex, `Type of skill`, TimePeriod) %>%
    mutate(
        Value = as.numeric(Value)
    ) %>%
    ggplot(aes(x = Value)) +
    geom_boxplot()

```

## Data Wrangling: Subsetting through filter()

Now that we've examined potential outliers (and found none), we might want to **subset** our data to make our work (i.e., exploring/analyzing/visualizing) more *manageable*. 

We can begin asking specific questions of our data. What if we wanted to find proportion of Youth/Adult with ICT skills by Country & Gender?

We'll quickly find that we need more specific questions with `filter()`

# NOTE: Get re-acquainted with meta-data. 


```{r,include=FALSE}

# We need more specific questions. We can do this by using filter()

# What if we wanted proportion of Gender & ICT Skills for Thailand in 2018?

data %>%
    # select specific columns (de-select others)
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    # rename column
    rename(type_of_skill = `Type of skill`) %>%
    # mutate creates new column
    mutate(
        Value = as.double(Value)
    ) %>%
     # filter on condition within parentheses
    filter(GeoAreaName == 'Thailand') %>% 
    filter(TimePeriod == 2018) %>% 
    arrange(desc(Value))

# NOTE: Here we see that for Thailand in 2018, in terms of ICT SKills and Gender, the highest proportion were Women and the COPA skill. Followed closely by WOmen and CMFL skill. 

```

## Data Wrangling: Aggregate data by using group_by(), summarize(), arrange()

Previously, by filtering for GeoAreaName ("Thailand") and TimePeriod ("2018"), we saw detailed ranking of proportion of population with sub-types of ICT Skill and gender. Perhaps we want to step back and look at data in the **aggregate**.

What if we wanted to aggregate across Gender (Male, Female, Bothsex), we want to look at the aggregate proportion ranked by ICT Skills, for Thailand in 2018?

# NOTE: Get re-acquainted with meta-data. 

```{r,include=FALSE}

# What if we aggregate across Gender (Male, Female, Bothsex), we want to look at the aggregate proportion ranked by ICT Skills, for Thailand in 2018?


data %>%
    # select specific columns (de-select others)
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    # rename column
    rename(type_of_skill = `Type of skill`) %>%
    # mutate creates new column
    mutate(
        Value = as.double(Value)
    ) %>%
     # filter on condition within parentheses
    filter(GeoAreaName == 'Thailand') %>% 
    filter(TimePeriod == 2018) %>% 
    # group_by
    group_by(type_of_skill) %>%
    # When aggregating across Gender within a Year, we'll Sum proportion
    summarize(
        sum_value = sum(Value)
    ) %>%
    ungroup() %>%
    # arrange
    arrange(desc(sum_value))

# NOTE: we see that more of the population does COPA, followed by CMFL, PCPR trailing. 
```

## Data Wrangling: Aggregating across TimePeriod

Previously, we aggregated across Gender for a specific year ("2018"). What if we wanted to aggregate across years (2014 & 2018), 

```{r,include=FALSE}

data %>%
    # select specific columns (de-select others)
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    # rename column
    rename(type_of_skill = `Type of skill`) %>%
    # mutate creates new column
    mutate(
        Value = as.double(Value)
    ) %>%
     # filter on condition within parentheses
    filter(GeoAreaName == 'Thailand') %>% 
    # We take OUT the TimePeriod filter for a specific year
    # But we'll add TimePeriod to group_by
    group_by(type_of_skill, TimePeriod) %>%
    # When aggregating across years, it makes more sense to find average Value (not Sum)
    summarize(
        sum_value = sum(Value)
    ) %>%
    ungroup() %>%
    # arrange first by sum_value
    # then also by TimePeriod (sorting by multiple columns)
    arrange(desc(sum_value)) %>%
    arrange(desc(TimePeriod))

# What if we wanted to sum across both years (2014 & 2018)
# Take out TimePeriod
# Change sum_value to mean_value
    

```

## Even More Specific

First we looked at Thailand in 2018, across Gender. Now, what if we wanted to focus specifically on WOMEN with various ICT skills


```{r,include=FALSE}

data %>%
    # select specific columns (de-select others)
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    # rename column
    rename(type_of_skill = `Type of skill`) %>%
    # mutate creates new column
    mutate(
        Value = as.double(Value)
    ) %>%
     # filter on condition within parentheses
    filter(GeoAreaName == 'Thailand') %>% 
    # filter on gender
    filter(Sex=='FEMALE') %>%
    # We take OUT the TimePeriod filter for a specific year
    # But we'll add TimePeriod to group_by
    group_by(type_of_skill, TimePeriod) %>%
    # When aggregating across years, it makes more sense to find average Value (not Sum)
    summarize(
        sum_value = sum(Value)
    ) %>%
    ungroup() %>%
    # arrange first by sum_value
    # then also by TimePeriod (sorting by multiple columns)
    arrange(desc(sum_value)) %>%
    arrange(desc(TimePeriod))

# NOTE: When adding filter(Sex=='FEMALE'), the TimePeriod shows only 2018
# Also examing filter(s) from the View() of data

```

## Examining Data Across Countries

We'll now use the functions we've learned to zoom out and examine proportion of population with various ICT Skills **across** type_of_skill, gender and time; making these comparisons between countries.

```{r,include=FALSE}

data %>%
    # select specific columns (de-select others)
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    # rename column
    rename(type_of_skill = `Type of skill`) %>%
    # mutate creates new column
    mutate(
        Value = as.double(Value)
    ) %>%
    # instead of filtering, jump to group_by
    group_by(GeoAreaName) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    ungroup() %>%
    arrange(desc(mean_value))

# If we start at most macro-level across gender, type_of_skill and time. We'll only group_by(GeoAreaName).

```


## Asking Specific Questions of the Data

The most important thing we can do as an analyst is to be able to pose questions of our data. Here are some specific questions we could ask:

```{r,include=FALSE}

# Which countries did the best for women acquiring ICT Skills in 2017 ?

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>% 
    mutate(
        Value = as.numeric(Value)
    ) %>%
    group_by(GeoAreaName, Sex, TimePeriod) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    arrange(desc(mean_value)) %>%
    filter(TimePeriod==2017) %>%
    filter(Sex=='FEMALE')

# How about women acquiring ICT Skills over the entire time period (2014 - 2019)?

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>% 
    mutate(
        Value = as.numeric(Value)
    ) %>%
    # to summarize over extended time period, remove TimePeriod from group_by
    group_by(GeoAreaName, Sex) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    arrange(desc(mean_value)) %>%
    filter(Sex=='FEMALE')

# YOUR TURN: Which countries did the best for men acquiring ICT Skills in 2016?

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>% 
    mutate(
        Value = as.numeric(Value)
    ) %>%
    group_by(GeoAreaName, Sex, TimePeriod) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    arrange(desc(mean_value)) %>%
    filter(TimePeriod==2016) %>%
    filter(Sex=='MALE')

# YOUR TURN: How about over the entire time period?

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>% 
    mutate(
        Value = as.numeric(Value)
    ) %>%
    group_by(GeoAreaName, Sex) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    arrange(desc(mean_value)) %>%
    filter(Sex=='MALE')

# YOUR TURN: Which countries did the best for both sex in acquiring ICT Skills in 2015?


data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>% 
    mutate(
        Value = as.numeric(Value)
    ) %>%
    group_by(GeoAreaName, Sex, TimePeriod) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    arrange(desc(mean_value)) %>%
    filter(TimePeriod==2015) %>%
    filter(Sex=='BOTHSEX')


# YOUR TURN: How about over the entire time period?

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>% 
    mutate(
        Value = as.numeric(Value)
    ) %>%
    group_by(GeoAreaName, Sex) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    arrange(desc(mean_value)) %>%
    filter(Sex=='BOTHSEX')

```

## Asking Specific Question: Specific ICT Skills Breakdown

```{r,include=FALSE}

# Which countries, across time, did the best (% of population) for EMAIL specifically?

data %>%
    select(GeoAreaName, Value, Sex, `Type of skill`, TimePeriod) %>%
    rename(type_of_skill = `Type of skill`) %>% 
    mutate(
        Value = as.numeric(Value)
    ) %>%
    group_by(GeoAreaName) %>%
    filter(type_of_skill=='EMAIL') %>%
    arrange(desc(Value)) %>%
    summarize(
        mean_value = mean(Value)
    ) %>%
    arrange(desc(mean_value))

# Which countries had the most "TimePeriod"(s) recorded? (As in tally)

data %>%
    select(GeoAreaName, TimePeriod) %>%
    group_by(GeoAreaName, TimePeriod) %>%
    tally(sort = TRUE) %>%
    summarize(
        sum_n = sum(n)
    ) %>%
    arrange(desc(sum_n))

```


## TIDY DATA PRINCIPLE: Spread & Pivot_Wider

